Machine Learning Model for Agricultural Data Applications

### 2021-03-13 chapters/implementation.tex
Added Python Code File

\section{Data Science - Engineering}

The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}

>>>>

\section{Data Science - Engineering}
\todo{Demonstrate the ability for analysis.}
\todo{Link to Related works - Not repeating. Might look at the sections and link them}

\todo{Section 1 is very interesting and further supports, or cast doubts or raises question marks about what is being said in the Related works.}
The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}

### 2021-03-13 chapters/methods.tex
Layouts
Added Python Code File

\section{Data Science}
Data Science is a subset of Computer Science and Mathematics. This subset introduces a new paradigm which creates algorithms for computers and robots. It combines statistics with Computer Science. Data Science also involves the use of machine learning algorithms for prediction.

@@

>>>>

\section{Data Science}

\todo{It's critical that this section JUSTIFIES THE TOOLS I'm using. Think of a plumber.}

\todo{I'll have to JUSTIFY my approach}

\todo{I'll have to justify why I am selecting certain tools to answer my Research questions. That is the questions in the Diagram in Related Works}

\todo{In addition, extract questions that go into a table. Justify why you have selected the sections and reference the Literature review. Maybe not relevant to my work.}
Data Science is a subset of Computer Science and Mathematics. This subset introduces a new paradigm which creates algorithms for computers and robots. It combines statistics with Computer Science. Data Science also involves the use of machine learning algorithms for prediction.

@@

Testing my commit
